rr

### 2025-11-21 double_elimination.qmd
updates

  if (distribution == "Normal") {
    strengths <- sapply(num_teams, function(n) {
      qnorm(1:n/(n+1))
    })
    normal_strengths <- data.frame(
      true_rank = as.numeric(teams),
      true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
      rank_hat = rep(NA, length(teams)),
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams))
    )
    df <- arrange(normal_strengths, true_rank)
  } else if (distribution == "Uniform") {
    strengths <- sapply(num_teams, function(n) {
      qunif(1:n/(n+1), 0, sqrt(12))
    })
    unif_strength <- data.frame(
      true_rank = as.numeric(teams),
      true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams)),
      rank_hat = rep(NA, length(teams))
    )
    df <- arrange(unif_strength, true_rank)
  } else if (distribution == "Same"){
    strengths <- sapply(num_teams, function(n) {rep(0,n)})
    normal_strengths <- data.frame(
      true_rank = as.numeric(teams),
      true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
      rank_hat = rep(NA,length(teams)),
      game_wins = rep(0,length(teams)),
      game_losses = rep(0,length(teams))
    )
    df <- arrange(normal_strengths, true_rank)
  } else if (distribution == "Manual") {
    strengths <- theta_hat
    manual_strengths <- data.frame(
      true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
      rank_hat = rep(NA, length(teams)),
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams))
    )
    df <- manual_strengths %>%
      arrange(true_strength) %>%
      mutate(true_rank = as.numeric(teams)) %>%
      arrange(true_strength, true_rank)
  } else {
    stop("Distribution not found: Enter Manual to input your own strengths")
  }

>>>>

  if (distribution == "Normal") {
    strengths <- sapply(num_teams, function(n) {
      qnorm(1:n/(n+1))
    })
    normal_strengths <- data.frame(
      true_rank = as.numeric(teams),
      true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
      rank_hat = rep(NA, length(teams)),
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams))
    )
    df <- arrange(normal_strengths, true_rank)
  } else if (distribution == "Uniform") {
    strengths <- sapply(num_teams, function(n) {
      qunif(1:n/(n+1), 0, sqrt(12))
    })
    unif_strength <- data.frame(
      true_rank = as.numeric(teams),
      true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams)),
      rank_hat = rep(NA, length(teams))
    )
    df <- arrange(unif_strength, true_rank)
  } else if (distribution == "Same"){
    strengths <- sapply(num_teams, function(n) {rep(0,n)})
    normal_strengths <- data.frame(
      true_rank = as.numeric(teams),
      true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
      rank_hat = rep(NA,length(teams)),
      game_wins = rep(0,length(teams)),
      game_losses = rep(0,length(teams))
    )
    df <- arrange(normal_strengths, true_rank)
  } else if (distribution == "Exponential"){
      strengths <- sapply(num_teams, function(n) { qexp(1:n/(n+1)) })
      unif_strength <- data.frame(
        true_rank = as.numeric(teams),
        true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
        game_wins = rep(0,length(teams)),
        game_losses = rep(0,length(teams)),
        rank_hat = rep(NA,length(teams))
      )
      df <- arrange(unif_strength, true_rank)
  } else if (distribution == "Manual") {
    strengths <- theta_hat
    manual_strengths <- data.frame(
      true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
      rank_hat = rep(NA, length(teams)),
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams))
    )
    df <- manual_strengths %>%
      arrange(true_strength) %>%
      mutate(true_rank = as.numeric(teams)) %>%
      arrange(true_strength, true_rank)
  } else {
    stop("Distribution not found: Enter Manual to input your own strengths")
  }

### 2025-11-21 group_stage.qmd
updates

  # Create team strengths based on distribution
  if (distribution == "Normal"){
    strengths <- sapply(num_teams, function(n) { qnorm(1:n/(n+1)) })
    team_strengths <- data.frame(
      true_rank = as.numeric(teams),
      theta = strengths,
      rank_hat = rep(NA, length(teams)),
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams))
    )
    df <- arrange(team_strengths, true_rank)
  }
  else if (distribution == "Same"){
    strengths <- sapply(num_teams, function(n) {rep(0, n)})
    team_strengths <- data.frame(
      true_rank = as.numeric(teams),
      theta = strengths,
      rank_hat = rep(NA, length(teams)),
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams))
    )
    df <- arrange(team_strengths, true_rank)
  }
  else if (distribution == "Uniform"){
    strengths <- sapply(num_teams, function(n) { qunif(1:n/(n+1), 0, sqrt(12)) })
    team_strengths <- data.frame(
      true_rank = as.numeric(teams),
      theta = strengths,
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams)),
      rank_hat = rep(NA, length(teams))
    )
    df <- arrange(team_strengths, true_rank)
  }
  else if (distribution == "Manual") {
    strengths <- theta_hat
    manual_strengths <- data.frame(
      theta = strengths,  # Also renamed to match other distributions
      rank_hat = rep(NA, length(strengths)),
      game_wins = rep(0, length(strengths)),
      game_losses = rep(0, length(strengths))
    )
    df <- manual_strengths %>% 
      arrange(desc(theta)) %>%
      mutate(true_rank = row_number()) %>%
      arrange(true_rank)
  }
  else {
    stop("Distribution not found: Enter Manual to input your own strengths")
  }

>>>>

  # Create team strengths based on distribution
  if (distribution == "Normal"){
    strengths <- sapply(num_teams, function(n) { qnorm(1:n/(n+1)) })
    team_strengths <- data.frame(
      true_rank = as.numeric(teams),
      theta = strengths,
      rank_hat = rep(NA, length(teams)),
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams))
    )
    df <- arrange(team_strengths, true_rank)
  }
  else if (distribution == "Same"){
    strengths <- sapply(num_teams, function(n) {rep(0, n)})
    team_strengths <- data.frame(
      true_rank = as.numeric(teams),
      theta = strengths,
      rank_hat = rep(NA, length(teams)),
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams))
    )
    df <- arrange(team_strengths, true_rank)
  }
  else if (distribution == "Uniform"){
    strengths <- sapply(num_teams, function(n) { qunif(1:n/(n+1), 0, sqrt(12)) })
    team_strengths <- data.frame(
      true_rank = as.numeric(teams),
      theta = strengths,
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams)),
      rank_hat = rep(NA, length(teams))
    )
    df <- arrange(team_strengths, true_rank)
  } 
  else if (distribution == "Exponential"){
      strengths <- sapply(num_teams, function(n) { qexp(1:n/(n+1)) })
      unif_strength <- data.frame(
        true_rank = as.numeric(teams),
        true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
        game_wins = rep(0,length(teams)),
        game_losses = rep(0,length(teams)),
        rank_hat = rep(NA,length(teams))
      )
      df <- arrange(unif_strength, true_rank)
  }    
  else if (distribution == "Manual") {
    strengths <- theta_hat
    manual_strengths <- data.frame(
      theta = strengths,  # Also renamed to match other distributions
      rank_hat = rep(NA, length(strengths)),
      game_wins = rep(0, length(strengths)),
      game_losses = rep(0, length(strengths))
    )
    df <- manual_strengths %>% 
      arrange(desc(theta)) %>%
      mutate(true_rank = row_number()) %>%
      arrange(true_rank)
  }
  else {
    stop("Distribution not found: Enter Manual to input your own strengths")
  }

### 2025-11-21 round_robin.qmd
Saved Single Elimination and Double Elimination Simulations
.
updates

  # Initialize strength vector
  if (distribution == "Normal") {
    strengths <- qnorm(1:num_teams / (num_teams + 1))
  } else if (distribution == "Same") {
    strengths <- rep(0, num_teams)
  } else if (distribution == "Uniform") {
    strengths <- qunif(1:num_teams / (num_teams + 1), 0, sqrt(12))
  } else if (distribution == "Manual") {
    if (is.null(theta_hat)) {
      stop("theta_hat must be provided for Manual distribution")
    }
    strengths <- theta_hat
  } else {
    stop("Distribution not found: Enter Manual to input your own strengths")
  }

@@

simulate_roundrobin_r(16,"Normal", r = 4)
```

>>>>

  # Initialize strength vector
  if (distribution == "Normal") {
    strengths <- qnorm(1:num_teams / (num_teams + 1))
  } else if (distribution == "Same") {
    strengths <- rep(0, num_teams)
  } else if (distribution == "Uniform") {
    strengths <- qunif(1:num_teams / (num_teams + 1), 0, sqrt(12))
  } else if (distribution == "Exponential") {
    strengths <- qexp(1:num_teams / (num_teams + 1), 1)
  } else if (distribution == "Manual") {
    if (is.null(theta_hat)) {
      stop("theta_hat must be provided for Manual distribution")
    }
    strengths <- theta_hat
  } else {
    stop("Distribution not found: Enter Manual to input your own strengths")
  }

@@

simulate_roundrobin_r(16,"Normal", r = 1)
```
